
\documentclass[letterpaper,10.8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-1pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt} \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      #3  &  #4 \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label={$\diamond$}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------

  \textbf{\LARGE Jeremy Welsh}\\
  \vspace{1pt}
Computational Scientist\\

\vspace{5pt}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
Email : \href{mailto:jeremy@micromelody.net}{jeremy@micromelody.net} & Linkedin: \href{http://www.linkedin.com/in/jeremy-welsh}{www.linkedin.com/in/jeremy-welsh}  \\
Mobile : +1 (503) 890-1543  & Github: \href{https://github.com/jeremyiwk}{github.com/jeremyiwk}
\end{tabular*}
\vspace{-12pt}\\
%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Programming Languages}{Python, C++, Julia, Fortran, Bash, R, SQL, Mathematica}
	\resumeSubItem{Frameworks}{NumPy, Pandas, SciPy, Scikit-Learn, TensorFlow, OpenCV, OpenMP, MPI, MDTraj, Matplotlib, Numba}
	\resumeSubItem{Software \& Tools}{Git, Jira, General Particle Tracer (GPT), GROMACS, LAMMPS, Slurm}
\resumeSubHeadingListEnd 

%


%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
  
  
    \resumeSubheading
    {Computational Scientist}{Feb 2024 – Present}{Thermo Fisher Scientific}{Remote / Hillsboro, OR}
    
    \begin{itemize}[leftmargin=*,label={$\diamond$}]
    \itemsep0em %{description} [font=$\bullet$]
    
    	\item {Developed scientific software in an Agile environment with a team of scientists and software engineers to model and optimize Focused Ion Beam (FIB) optics and beam interactions with materials.}
	
	\item {Developed workflows for discretizing FIB column elements for use in boundary element method solvers.}
	
	\item {Developed algorithms for internal state modeling and adaptive control of FIB systems.}
	
	\item {Optimized algorithms for computing numerical solutions to Hamilton-Jacobi type equations.}
	
	\item {Served as system administrator for local high performance computing cluster.}
	
	\end{itemize} %{description}
  
   \resumeSubheading
    {Private Tutor}{Aug 2023 – Present}{LA Tutors 123}{Remote}
    
    \begin{itemize}[leftmargin=*,label={$\diamond$}]
    \itemsep0em %{description} [font=$\bullet$]
    
    	\item {Provided remote math tutoring for college students in algebra, pre-calculus, and calculus.}
	
	\end{itemize} %{description}
  
    \resumeSubheading
    {Senior Intern}{Jun 2022 – Jun 2023}{Thermo Fisher Scientific}{Remote / Hillsboro, OR}
    
    \begin{itemize}[leftmargin=*,label={$\diamond$}]
    \itemsep0em %{description} [font=$\bullet$]
    
    	\item {Developed Python code to automate machine control for milling and imaging workflows on dual-beam (FIB-SEM) microscope systems.}
	
	\item {Designed experiments and computer vision image analysis to detect $\sim$100nm machining tolerances in FIB column.}
	
	\item {Developed Python code to measure optical aberrations in ion beam using computer vision tools from OpenCV and Skimage.}
	
	\item {Designed simulation components in C for ion column simulations in the General Particle Tracer software package.}
	
	\item {Developed scientific software in Python for parallelizing simulations and data analysis in HPC environments.}
	
	\item {Developed algorithms to optimize ion column designs, resulting in up to 350\% improvement in ion beam performance for some applications.}
	
	\item {Created data visualizations and presentations of algorithm design, experimental design, and results to a team of scientists in order to direct critical decisions about focused ion beam R\&D.}
	
	\end{itemize} %{description}
      
    \resumeSubheading
		{Graduate Research Assistant / Graduate Teaching Assistant}{Sep 2020 – Jun 2022}
		{University of Oregon}{Eugene, OR}
	\begin{itemize}[leftmargin=*,label={$\diamond$}]
	\itemsep0em  %{description} [font=$\bullet$]
	
	%\item{Developed theoretical models for organic macromolecules at multiple resolutions using mathematical tools from non-equilibrium statistical mechanics.}
	
	\item{Developed coarse-grained models of DNA and proteins, and validated models using molecular dynamics simulations (GROMACS and LAMMPS) and Monte Carlo simulations.}
	
	%\item{Validated theoretical models against experimental data using molecular dynamics and Monte Carlo simulation data.}
	
	\item{Wrote scripts in Python and Bash for performing molecular dynamics simulations using GROMACS and LAMMPS molecular dynamics software on HPC clusters at San Diego Supercomputer Center.}
	
	\item{Characterized performance and degree of parallelism of simulation software to determine computational resource requirement on 128 Core/node HPC system.}

	\item{Developed data analysis tools in Python, Fortran, and C++ for data analysis of $\sim$10TB of molecular dynamics simulation data.}
	
	%\item{Wrote Fortran code to create input data for polymers of arbitrary length for MCCCS Towhee Monte Carlo molecular simulation software}
	
	%\item{Used clustering algorithms, such as DBSCAN, to determine coordinate regions for Markov Chain Monte Carlo simulation.}
	
	%\item{Validated coarse-grained molecular models against statistical models such as principal component analysis (PCA) and time-lagged independent component analysis (t-ICA).}
	
	\item{Mentored undergraduate and graduate research assistants on code development, simulation data analysis, and theoretical molecular biophysics.}
	
	\item {Instructed tutorials and labs in undergraduate physics courses on electricity and magnetism, circuitry, Newtonian mechanics, and computational chemistry.}
	
	
	\end{itemize} %{description}
	
  


    
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {M.S., Physics}{Sep 2020 - Jun 2022}
      {University of Oregon, GPA: 3.92}{Eugene, OR}
      
%	   {\scriptsize \textit{Courses: Operating Systems, Analysis Of Algorithms, Artificial %Intelligence, Machine Learning, Probability and Statistics and Network Security.}}
	   
    \resumeSubheading
      {B.S., Mathematics and Physics}{Sep 2016 - June 2020}
      {University of Oregon, GPA: 3.83 }{Eugene, OR}
  \resumeSubHeadingListEnd


  %\resumeSubheading
    %{Graduate Teaching Assistant}{Mar 2022 - Jun 2022}
   % {University of Oregon}{Eugene, OR}
    
    %\begin{itemize}[leftmargin=*,label={$\diamond$}]
    %\itemsep0em  %{description} [font=$\bullet$]
	%\item {Instructed tutorials and labs in undergraduate physics courses covering electricity and magnetism, circuitry, and Newtonian mechanics.}

	%\end{itemize} %{description}
	
	%\resumeSubheading
    %{Library Student Assistant}{Sep 2017 - Jun 2022}
    %{University of Oregon}{Eugene, OR}
    
    %\begin{itemize}[leftmargin=*,label={$\diamond$}]
    %\itemsep0em %{description} [font=$\bullet$]
    %\item {Provided tutoring for math and science subjects including: algebra, probability and statistics, calculus, differential equations, linear algebra, and computer science.}
	%\item {Trained library student employees on techniques for tutoring elementary and advanced mathematical topics and concepts.}
	%\item {Assisted library patrons with use of library services and systems.}
	%\end{itemize} %{description}


%-----------PROJECTS-----------------
%\section{Academic Projects}


%-----------Awards-----------------
%\section{Awards and Honors}
%\begin{description}[font=$\bullet$]
%\item {Departmental Honors in Physics} 
%\item {Latin Honors, Cum Laude}
%\item {Phi Beta Kappa Honors Society}
%\end{description}
%-------------------------------------------
\end{document}